% !TEX program = xelatex
% general resume
% by EULIR

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{RUNMING LI}

\basicInfo{
  \email{runmingli\_edu@163.com} \textperiodcentered\ 
  \phone{(+86) 139-8001-6050} \textperiodcentered\ 
  \github[EULIR]{https://github.com/EULIR} \textperiodcentered\ 
  \linkedin[RUNMING LI]{www.linkedin.com/in/runming}
  }

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Chengdu No.7 High School Linyin Campus}, Sichuan, China}{Sep. 2017 -- Current}

\section{\faGithubAlt\ Personal Projects}

\datedsubsection{\textbf{EULIR Extended Math Library}}{\url{https://github.com/EULIR/Extended-Math-Library}}
Math API under JVM.
\begin{itemize}
  \item Implements mathematical formulas and expressions natively.
  \item Contains statistical formulas and calculations.
  \item Unit test driven library, covering 100 percent classes; uses JUnit Framework.
  \item JavaDoc page on {\url{https://eulir.github.io/eeml}}.
\end{itemize}

\datedsubsection{\textbf{Project Euler}}{\url{https://github.com/EULIR/PROJECT-EULER}}
Java solutions to Project Euler.
\begin{itemize}
  \item Contains Java solutions to more than 100 project Euler problems.
  \item Ranked top 1 percent across the site.
\end{itemize}

%\datedsubsection{\textbf{CAPTCHAs-Solver}}{\url{https://github.com/EULIR/CAPTCHAs-Solver}}
%Captcha slover written in Python.
%\begin{itemize}
%  \item Light captcha solver, containing only four py files.
%  \item Allows vague recognition.
%  \item Able to recognize alphabets and figures.
%  \item 4 characters recognition supported currently.
%\end{itemize}

\datedsubsection{\textbf{Brainf**k Interpreter}}{\url{https://github.com/EULIR/Brainfuck-interpreter}}
Interpreter for Brainf**k programming language written in Java.
\begin{itemize}
  \item Interprets brainf**k syntax 100\% correct.
  \item Contains syntactic errors detection mechanism.
\end{itemize}

\datedsubsection{\textbf{Form Drawer}}{\url{https://github.com/GreatChina-CSClub/form-drawer}}
Simple form drawer for data visualization.
\begin{itemize}
  \item Supports historgram and line chart in both simple and layered form.
  \item Write to file mode enabled, generating images in various type.
  \item Pictures can be dynamically resized.
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Programming Languages}:
    skilled at Java; experienced in Kotlin/Python/C/Pascal; four years experience of programming with at least one year in each programming language.
  \item \textbf{Website Design}:
    experienced in HTML/CSS, personal sites including {\url{http://www.neofuture.tech}} and {\url{http://www.cmstation.cn}}.
  \item \textbf{Developing Tools}:
    can adapt to any editors/OSs, normally use JetBrains IDEs and Notepad++ under Windows and CentOS; have experience with team tools like git, GitHub, Coding.net.
  \item \textbf{Compiler}:
    understand basic level complier， including principles, techniques, and tools. 
  \item \textbf{Statistics}:
    one year of college level statistics experience.
\end{itemize}

\section{\faHeartO\ Achievements}
\datedline{\textbf{Top 1 percent} on \href{https://projecteuler.net} {Project Euler} across the whole site}{Mar. 2018}

%\section{\faUsers\ Standardized Test Score}
%\begin{itemize}[parsep=0.5ex]
%  \item \textbf{Advanced Placement}: Computer Science A: 5 (year of 2018); Statistics: 5 (year of 2018).
%  \item \textbf{TOEFL}:108
%  \item \textbf{SAT}:1470
%\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  %\item Blog: \url{https://eulir.github.io/}
  \item Opensource contributions: more than 700 contributions in the past one year on GitHub \url{https://eulir.github.io/open-source-contribution/} 
    see also {\url{https://github.com/EULIR}}
  \item Languages: English - professional working proficiency (TOEFL 111), Mandarin Chinese - native speaker
  \item Intended position: software development internship
  \item Get the latest version of this resume: \url{https://tinyurl.com/eulir-resume}
\end{itemize}

\end{document}
