% !TEX program = xelatex
% general resume
% by EULIR

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{ANDY EULIR LI}

\basicInfo{
  \email{runmingli\_edu@163.com} \textperiodcentered\ 
  \phone{(+86) 139-8001-6050} \textperiodcentered\ 
  \github[EULIR]{https://github.com/EULIR} %\textperiodcentered\ 
  %\linkedin[EULIR LI]{http://www.linkedin.com/in/eulir-li-130a3b166/}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Chengdu No.7 High School}, Sichuan, China}{Sep. 2017 -- Present}

\section{\faGithubAlt\ Personal Projects}
\datedsubsection{\textbf{EULIR Extended Math Library}}{\url{https://github.com/EEML/Extended-Math-Library}}
Math API under JVM.
\begin{itemize}
  \item Implements mathematical formulas and expressions natively.
  \item Contains statistical formulas and calculations.
  \item Test-driven library, covering 100 percent classes.
  \item Keeps updating.
\end{itemize}

\datedsubsection{\textbf{Project Euler}}{\url{https://github.com/EULIR/PROJECT-EULER}}
Java solutions to Project Euler.
\begin{itemize}
  \item Contains Java solutions to more than 100 project euler problems.
  \item Ranked top 1 percent across the site.
  \item Written in Java10, under the Oracle's latest release.
\end{itemize}

\datedsubsection{\textbf{CAPTCHAs-Solver}}{\url{https://github.com/EULIR/CAPTCHAs-Solver}}
Captcha slover written in Python.
\begin{itemize}
  \item light captcha solver(contains only four py files).
  \item allows vague recognition.
  \item able to recognize alphabets and figures.
  \item 4 characters supported currently.
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Programming Languages}:
    experienced in Java/Kotlin/Pascal/Python/Brainf**k, especially mastered in Java.
  \item \textbf{Website Design}:
	experienced in HTML/CSS, especially mastered in website design under GitHub page.
  \item \textbf{Editors}:
    normally use JetBrains IDEs, Notepad++.
  \item \textbf{AP}:
    experienced in all stuff about AP Computer Science A course.
  \item \textbf{Public Speaking}:
	\begin{itemize}[parsep=0.5ex]
	  \item acting leader/tutor of a Computer Science club.
	  \item 2 times NHSDLC top speakers.
	\end{itemize}
\end{itemize}

\section{\faHeartO\ Achievements}
\datedline{\textbf{Top 1 percent} on \href{https://projecteuler.net} {Project Euler} across the whole site}{Mar. 2018}

\section{\faUsers\ Standardized Test Score}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Advanced Placement}
	  \begin{itemize}[parsep=0.5ex]
		  \item Computer Science A: 5
		  \item Statistics: 5
	  \end{itemize}
  \item \textbf{TOEFL}
		\begin{itemize}[parsep=0.5ex]
		  \item Reading 27
		  \item Listening 26
		  \item Speaking 27
		  \item Writing 28
		  \item Total 108
	  \end{itemize}
  \item \textbf{SAT}
		\begin{itemize}[parsep=0.5ex]
		  \item Reading Test
		  \item Writing and Language Test
		  \item Math Test
		  \item Total
		  \item Writing
	  \end{itemize}
\end{itemize}	

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: \url{https://eulir.github.io/}
  \item Opensource contributions: \url{https://eulir.github.io/open-source-contribution/} 
  \item Languages: English - fluent, Chinese - native speaker
  \item Get the latest version of this resume: \url{https://tinyurl.com/eulir-resume}
\end{itemize}

\end{document}
